---
title: "Introduction to binomial"
author: Pedram Doroudchi
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(binomial)
```

## binomial

The package `"binomial"` provides useful tools for computing and vizualizing a Binomial distribution given a certain number of trials and probability value.  

### Getting basic statistics from a binomial distribution

Finding the number of combinations in which *k* successes can occur in *n* trials:  

```{r}
combinations <- bin_choose(n = 5, k = 2)
combinations
```

Calculate the probability of getting *k* successes in *n* trials assuming a specified probability *p*:  

```{r}
prob <- bin_probability(success = 2, trials = 5, prob = 0.5)
prob
```

Compute the expected value, or the expected number of successes in n trials:  

```{r}
mean <- bin_mean(trials = 10, prob = 0.3)
mean
```

Compute the expectation of the squared deviation from the mean:

```{r}
var <- bin_variance(trials = 10, prob = 0.3)
var
```

Compute the most likely number of success in *n* independent trials with probability *p*:  

```{r}
mode <- bin_mode(trials = 10, prob = 0.3)
mode
```

Calculate the asymmetry of the probabiltiy distribution about its mean:  

```{r}
skew <- bin_skewness(trials = 10, prob = 0.3)
skew
```

Calculate the "tailedness", or shape, of the probability distribution:  

```{r}
kurtosis <- bin_kurtosis(trials = 10, prob = 0.3)
kurtosis
```

### Getting a list of statistics

Print a binomial random variable list displaying the number of trials and probability of success:  

```{r}
bin1 <- bin_variable(10, 0.3)
bin1

# use summary() to print additional summary statistics such as mean, variance, etc.

binsum1 <- summary(bin1)
binsum1
```

### Tabular data and plotting options

Values of a probability distribution in data frame format:  

```{r}
dis1 <- bin_distribution(5, 0.5)
dis1

# plot probability histogram of binomial distribution

plot(dis1)
```

Calculate additional cumulative probabilties into data frame:  

```{r}
dis2 <- bin_cumulative(5, 0.5)
dis2

# plot cumulative distribution

plot(dis2)
```

